---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 12"
author: "Eric weah "
output: html_notebook
---

## Assigned Exercises

- DC Chapter 12 Exercises: 12.1,12.2,12.3,12.4

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(DataComputing)

```



## Chapter 12 Exercises

### Problem 12.1

a.)  BothSexes
```{r}
BothSexes <-
  BabyNames %>% 
  spread(key = sex, value = count)%>%
  filter(F>1,M>1)
 
```



b.)
```{r}
BothSexes %>%
  group_by(name)%>%
  mutate(genderBalance=abs(log(F/M)))%>%
  arrange(genderBalance)
```

c.)
```{r}
BothSexes %>%
  group_by(name)%>%
  mutate(genderBalance=abs(log(F/M)))%>%
  arrange(genderBalance)
```

### Problem 12.2
a.) version 1:  each case shows the popular baby name of a given year both female and male. also the total number of babies they had that year whihc helps shows the popularity.
version 2: each case represents  the count of both sexes, and seems to be in wide form
version 3: each case shows the year 1912 and 2012 and how many babies were born for both years.
b.) The command for version 2 is wider and  would look like
 spread(key=sex,value=nbabies).
  the spread function is used and the varibale sex is seperated in male and female for thier own columns.
c.) the cammand for version 1 is wider and would look like 
gather(key=year,value=count,"1912","2012").
the gather function is used and the years are condensed  to make year and count .
 
d.) version 3 because the years are their own columns .
e.) you can start using data verbs but it would be better to translate the table to version 2 because it will be easier to wrangle.
### Problem 12.3
a.) A versus C : A would be considered wide
    B versus C : B would be considered wide
    A versus B:  they are both considered wide
b.) data fram B
c.) data fram A 
### Problem 12.4
a.)  the subject column may be be collapsed down and make the table too narrow

b.) 
```{r}
BP_narrow %>%
  gather(key = when, value = sbp, before, after)
```

you can take out any one of the variables in the code, for example if i took out subject.